Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-09 cmsb22.tex
Some data on PyBoolNet repo

>>>>

\appendix

\section{Temporary}

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on the PyBoolNet's repository.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap-spaces) within the timeout of 2 minutes. Number in bold indicate a ratio greater than three.}
  \centering
  \label{tab:pyboolnet_repo}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $e$ & $s$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    arellano\_rootstem &&&& 4 & 0.04 & \textbf{0.31}\\
    calzone\_cellfate &&&& 27 & 0.03 & 0.08\\
    dahlhaus\_neuroplastoma &&&& 32 & 0.04 & 0.11\\
    davidich\_yeast &&&& 12 & 0.03 & 0.08\\
    dinwoodie\_life &&&& 7 & 0.03 & 0.08\\
    dinwoodie\_stomatal &&&& 1 & 0.04 & 0.05\\
    faure\_cellcycle &&&& 2 & 0.04 & 0.04\\
    grieco\_mapk &&&& 18 & 0.04 & 0.08\\
    irons\_yeast &&&& 1 & 0.05 & 0.04\\
    jaoude\_thdiff &&&& 1000+ & \textbf{1.73} & 0.40\\
    klamt\_tcr &&&& 8 & 0.06 & 0.04\\
    krumsiek\_myeloid &&&& 6 & 0.03 & 0.03\\
    multivalued &&&& 4 & 0.02 & 0.02\\
    n12c5 &&&& 5 & \textbf{34.37} & 0.06\\
    n3s1c1a &&&& 2 & 0.02 & 0.03\\
    n3s1c1b &&&& 2 & 0.02 & 0.03\\
    n5s3 &&&& 3 & 0.03 & 0.03\\
    n6s1c2 &&&& 3 & 0.03 & 0.04\\
    n7s3 &&&& 3 & 0.02 & 0.02\\
    raf &&&& 2 & 0.03 & 0.02\\
    randomnet\_n15k3 &&&& 3 & 0.04 & 0.05\\
    randomnet\_n7k3 &&&& 10 & 0.03 & \textbf{0.19}\\
    remy\_tumorigenesis &&&& 25 & \textbf{1.79} & 0.13\\
    saadatpour\_guardcell &&&& 1 & 0.02 & 0.03\\
    selvaggio\_emt &&&& 1000+ & \textbf{1.03} & 0.23\\
    tournier\_apoptosis &&&& 3 & 0.05 & 0.06\\
    xiao\_wnt5a &&&& 4 & 0.06 & 0.03\\
    zhang\_tlgl &&&& 156 & 0.26 & 0.17\\
    zhang\_tlgl\_v2 &&&& 258 & 0.19 & 0.17\\
    \bottomrule
  \end{tabular}

  \sylvain{I'm not sure that \(e\) and \(s\) are very relevant, moreover they are not readily available\dots}
\end{table}

As shown in Table~\ref{tab:pyboolnet_repo}, for most of the models of the official PyBoolNet repository\footnote{\url{https://github.com/hklarner/pyboolnet/tree/master/pyboolnet/repository}}, the results are comparable with all minimal trap spaces found very fast.
Note however that on some very small models, our proposed method was sometimes slower than PyBoolNet, but still way under one second.
Moreover, we believe that the result on the Arellano model is caused by the cold start of the JVM for BioLQM.
On the contrary, on every model that was a bit challenging for ByPoolNet, the new method was far more efficient with speedups between one and two orders of magnitude.
